Summary of Changes in response to Referee's Report

### 2015-11-28 curves-write-up/AIF/changes-summary.tex
responses to log stackiness comment of referee not being gorenstein

\begin{enumerate}
	\item We added a remark on Gorensteinness of the log canonical ring following
	the definition of a log spin canonical ring in the background section.
	\item Use Hilbert polynomial in Example $\_\_\_$
	\item Replace ``best lower approximation'' with Hirzebruch--Jung
		fractions
	\item (Not to-do yet) Change notation from $\frac{e_i - 1}{2 e_i}$
		to $\frac{e'_i}{2 e'_i + 1}$ where $e'_i = \frac{e_i - 1}{2}$ and
		we range over all $e'_i$ instead of odd $e_i$.
\end{enumerate}

>>>>

\begin{enumerate}
	\item We added a remark on Gorensteinness of the log canonical ring following
	the definition of a log spin canonical ring in the background section.
	We noticed in comment 1 that the referee made a comment saying
	``Cohen-Macaulay and
projectively Gorenstein follows as usual (of course, provided there are
no log canonical points).'' We were a bit confused about the parenthetical, but interpreted
it to mean that the canonical ring may not be Gorenstein if it is of the form
\begin{align*}
	\oplus_n H^0(X, P + n L)
\end{align*}
for $L$ some fractional divisor and $P$ a point. Of course, in our paper, all canonical rings are of the form
\begin{align*}
	\oplus_n H^0(X, n L)
\end{align*}
for $L$ a fractional divisor, so this would not pose an issue.
	\item Use Hilbert polynomial in Example $\_\_\_$
	\item Replace ``best lower approximation'' with Hirzebruch--Jung
		fractions
	\item (Not to-do yet) Change notation from $\frac{e_i - 1}{2 e_i}$
		to $\frac{e'_i}{2 e'_i + 1}$ where $e'_i = \frac{e_i - 1}{2}$ and
		we range over all $e'_i$ instead of odd $e_i$.
\end{enumerate}
